### 2015-02-20 fundamentals/impl.tex
misisng .

The current \Cycamore release provide basic functionality, As illustrated in
Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
functionality enabling simple fuel cycle analyses  As future contributions are
vetted, the capabilities in \Cycamore may grow.

>>>>

The current \Cycamore release provide basic functionality, As illustrated in
Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
functionality enabling simple fuel cycle analyses. As future contributions are
vetted, the capabilities in \Cycamore may grow.
